Deriving a precise Newtonian equation for the time it takes two separated bodies in an isolated system to collide due to the gravitational force

### 2022-10-30 paper/draft.tex
cleanup

where $p$ is the orbital period and $a$ is the semi-major axis. If we imagine two planets with an infinitesimally small radii but normal masses that have an orbit with an infinitesimally small semi-minor axis, so that the second planet would basically fall into the first, and reverse back into space by being slingshot after coming incredibly close to the center of gravity of the first; then the semi-major axis would basically be half of $R_i$ and the falling time from initial position would be half of the orbital period, therefore $p = 2\Delta T$ and $a = \frac{1}{2}R_i$. Substituting this in (20) and solving for $\Delta T$ we get

@@

    \Delta T_{s} =  \pi \sqrt{\frac{R_i^3}{8G(m_1 + m_2)}}

>>>>

where $p$ is the orbital period and $a$ is the semi-major axis. If we imagine two planets with infinitesimally small radii but normal masses that have an orbit with an infinitesimally small semi-minor axis, so that the second planet would basically fall into the first, and reverse back into space by being slingshot after coming incredibly close to the center of gravity of the first; then the semi-major axis would basically be half of $R_i$ and the falling time from initial position would be half of the orbital period, therefore $p = 2\Delta T$ and $a = \frac{1}{2}R_i$. Substituting this in (20) and solving for $\Delta T$ we get

@@

    \Delta T_{K} =  \pi \sqrt{\frac{R_i^3}{8G(m_1 + m_2)}}
